###Load the data

```{r, echo=TRUE}
data <- read.csv("activity.csv")
```

###Number of steps taken per day

```{r, echo=TRUE}
library(data.table)
tabledata <- data.table(data)
sum_date <- as.data.frame(tabledata[, sum(steps, na.rm = TRUE),by = date])
sum_date
```

###histogram of the total number of steps taken each day

```{r, echo=TRUE}
library(lattice)
histogram( ~ data$steps | data$date)
```


###Mean and median of the total number of steps taken per day

```{r, echo=TRUE}
tabledata <- data.table(data)
mean_date <- as.data.frame(tabledata[, mean(steps, na.rm = TRUE),by = date])
mean_date
median_date <- as.data.frame(tabledata[, as.numeric(median(steps, na.rm = TRUE)),by = date])
median_date
```

###Average number of steps taken by interval for all days

```{r, echo=TRUE}
mean_interval <- as.data.frame(tabledata[, mean(steps, na.rm = TRUE),by = interval])
mean_interval
plot(mean_interval,xlab = "interval", ylab = "average steps")
```

The maximum number of steps for an interval can be seen from the table above: 206 steps, corresponding to interval mumber 835.


###Calculate missing values

```{r, echo=TRUE}
dataw <- data[complete.cases(data),]
nrow(dataw)
```

###Imputing missing values and calculation of revised mean and median of the total number of steps taken per day

```{r, echo=TRUE}
data$steps[is.na(data$steps)] <- mean(data$steps, na.rm = TRUE)

tabledata <- data.table(data)
mean_date <- as.data.frame(tabledata[, mean(steps, na.rm = TRUE),by = date])
mean_date
median_date <- as.data.frame(tabledata[, as.numeric(median(steps, na.rm = TRUE)),by = date])
median_date
```

### Activity patterns between weekdays and weekends

```{r, echo=TRUE}

data$weekday <- weekdays(as.Date(data$date))

data$weekday[data$weekday=="Monday"] <- "weekday"
data$weekday[data$weekday=="Tuesday"] <- "weekday"
data$weekday[data$weekday=="Wednesday"] <- "weekday"
data$weekday[data$weekday=="Thursday"] <- "weekday"
data$weekday[data$weekday=="Friday"] <- "weekday"
data$weekday[data$weekday=="Saturday"] <- "weekend"
data$weekday[data$weekday=="Sunday"] <- "weekend"


datas1 <- subset(data, data$weekday=="weekday")
tabledata1 <- data.table(datas1)
mean_interval <- as.data.frame(tabledata1[, mean(steps, na.rm = TRUE),by = interval])
plot(mean_interval, xlab = "interval", ylab = "average steps", main="weekdays")


datas2 <- subset(data, data$weekday=="weekend")
tabledata2 <- data.table(datas2)
mean_interval <- as.data.frame(tabledata2[, mean(steps, na.rm = TRUE),by = interval])
plot(mean_interval,xlab = "interval", ylab = "average steps", main="weekend")

```

